Generate data for multispecies modeling, including diet!

### 2020-10-20 NOBAmsdiets.Rmd
fns readsurvs, lencomp; add survey lencomp plots

### Using the wrappers (now updated for annual age)

@@

@@

@@

# object in memory is no longer the same as saved files, need to read back into same configuration
# list of files in directory with surveyB.rds ending
# append to survObsBiom
# apply survey name from filename
survs <- list.files(path=d.name, pattern = "*surveyB.rds", full.names = TRUE)
survey.name <-  str_match(survs, paste0(scenario.name,"_\\s*(.*?)\\s*surveyB.rds"))[,2]
survObsBiom <- lapply(survs, readRDS)
names(survObsBiom) <- survey.name

@@

#### Survey length composition
```{r lencomp-1, eval=FALSE}

#length comps
len_comp_data <- readRDS(file.path(d.name, paste0(scenario.name, "survObsLenComp.rds")))
fish_len_comp_data <- readRDS(file.path(d.name, paste0(scenario.name, "fishObsLenComp.rds")))

len_comp_data <- len_comp_data[[1]]
fish_len_comp_data <- fish_len_comp_data[[1]]

@@

len <- filter(len_comp_data, time %in% c(55:175))

  lfplot <- ggplot(len, aes(upper.bins)) +
    geom_bar(aes(weight = atoutput)) +
    theme_tufte() +
    labs(subtitle = paste(scenario.name,
                          len$species))

  lfplot + facet_wrap(~time/stepperyr, ncol=6, scales="free_y")

@@

>>>>

### Using the wrappers (now updated for annual age, multiple surveys, and multispecies)

@@

Run notes: om_comps output took 4 hours for this group of 11 species with 2 surveys and 1 fishery.

@@

Now need a function to read survey-specific output files back into a single object with named surveys.

```{r readsurvs-function}

readsurvs <- function(path, type){

  datlook <- data.frame(dattype = c('survB', 'survAge', 'survLen', 'survWtage', 'survAnnAge', 'survAnnWtage'),
                        pattern = c("*surveyB.rds", "*survObsAgeComp.rds", "*survObsLenComp.rds", "*survObsWtAtAge.rds",
                                    "*survObsFullAgeComp.rds", "*survObsFullWtAtAge.rds"),
                        datname = c('survObsBiom', 'age_comp_data', 'len_comp_data', 'wtage', 'annage_comp_data', 'wtannage'))

  survs <- list.files(path=path, pattern = as.character(datlook$pattern[datlook$dattype %in% type]), full.names = TRUE)

  survey.name <-  str_match(survs, paste0(scenario.name,"_\\s*(.*?)\\s",datlook$pattern[datlook$dattype==type]))[,2]

  datname <- lapply(survs, readRDS)

  names(datname) <- survey.name

  return(datname)
}

Testing--read in the data for plotting:

```{r test-readurvs}

survObsBiom <- readsurvs(d.name, 'survB')
age_comp_data <- readsurvs(d.name, 'survAge')
len_comp_data <- readsurvs(d.name, 'survLen')
wtage <- readsurvs(d.name, 'survWtage')
annage_comp_data <- readsurvs(d.name, 'survAnnAge')
annage_wtage <- readsurvs(d.name, 'survAnnWtage')

Also need new plot functions and updated input file-writing functions that expect this structure.

@@

# object in memory is no longer the same as saved files, need to read back into same configuration
# list of files in directory with surveyB.rds ending
# append to survObsBiom
# apply survey name from filename
# survs <- list.files(path=d.name, pattern = "*surveyB.rds", full.names = TRUE)
# survey.name <-  str_match(survs, paste0(scenario.name,"_\\s*(.*?)\\s*surveyB.rds"))[,2]
# survObsBiom <- lapply(survs, readRDS)
# names(survObsBiom) <- survey.name

@@

#### Survey length composition
```{r lencomp-1}

#length comps
#len_comp_data <- readRDS(file.path(d.name, paste0(scenario.name, "survObsLenComp.rds")))

# now using readsurvs function above
# survs <- list.files(path=d.name, pattern = "*survObsLenComp.rds", full.names = TRUE)
# survey.name <-  str_match(survs, paste0(scenario.name,"_\\s*(.*?)\\s*survObsLenComp.rds"))[,2]
# len_comp_data <- lapply(survs, readRDS)
# names(len_comp_data) <- survey.name

fish_len_comp_data <- readRDS(file.path(d.name, paste0(scenario.name, "fishObsLenComp.rds")))

#len_comp_data <- len_comp_data[[1]]
fish_len_comp_data <- fish_len_comp_data[[1]]

@@

plotlen <- function(dat){

    ggplot(dat, aes(upper.bins)) +
    geom_bar(aes(weight = atoutput)) +
    theme_tufte() +
    labs(subtitle = paste(scenario.name,
                          dat$species)) +
    facet_wrap(~time/stepperyr, ncol=6, scales="free_y")

# len <- filter(len_comp_data, time %in% c(55:175))
# 
#   lfplot <- ggplot(len, aes(upper.bins)) +
#     geom_bar(aes(weight = atoutput)) +
#     theme_tufte() +
#     labs(subtitle = paste(scenario.name,
#                           len$species))
#   
#   lfplot + facet_wrap(~time/stepperyr, ncol=6, scales="free_y")

@@

##### `r names(len_comp_data)[1]`
``` {r, fig.show='hold'}
lcompsub <- as.data.frame(len_comp_data$BTS_fall_allbox_effic1[1]) %>% filter(time %in% c(55:175)) %>%
  group_by(species) %>%
  group_map(~ plotlen(.x), keep = TRUE)

for(i in 1:length(lcompsub)) {
  print(lcompsub[[i]])
}

#map(len_comp_data$BTS_fall_allbox_effic1 %>% keep(time %in% c(55:175)), plotlen)[[1]]
```

##### `r names(len_comp_data)[2]`
``` {r}
lcompsub <- as.data.frame(len_comp_data$BTS_spring_allbox_effic1[1]) %>% filter(time %in% c(55:175)) %>%
  group_by(species) %>%
  group_map(~ plotlen(.x), keep = TRUE)

for(i in 1:length(lcompsub)) {
  print(lcompsub[[i]])
}
```
